Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-06-06 paper/ms.tex
Un-did the example change.
Cleanups for title and abstract

\title{Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors}

@@

\begin{abstract}
The existence of ``hybrid" white dwarfs, made of a C/O
core within a O/Ne shell is accepted, and studies indicate that these are
viable progenitors for thermonuclear (type Ia) supernovae.
Recent work found that the C/O core is mixed with the surrounding O/Ne
as the white dwarf cools prior to accretion, which results in lower central
C fractions in the massive progenitor than previously assumed. To further
investigate the efficacy of hybrid white dwarfs as progenitors of
thermonuclear supernovae, we performed simulations of thermonuclear
supernovae from a new series of hybrid progenitors that include the
effects of cooling. The progenitor white dwarf model
was constructed with the one-dimensional stellar evolution code MESA and
represented a star evolved through the phase of unstable interior mixing
followed by accretion until it reached conditions for the ignition of
carbon burning. This MESA model was then mapped to a two-dimensional initial
condition and an explosion simulated with \FLASH. For comparison, a similar
simulation of an explosion was performed from a traditional C/O progenitor
white dwarf. By comparing the yields of the explosions, we found that as
with earlier studies, these hybrid models are viable supernova progenitors.
We contrast explosions from these models with explosions
from previous hybrid models
{\color{red} without the mixing during the white dwarf cooling}
and traditional C/O progenitors.
\end{abstract}

@@

Yo, hey Bubba!

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:conversion}
Estimated yield of \Ni{56} as a function of final mass burned to IGE
for C-O-Ne progenitors (red) and C-O progenitors (blue) at
$t = 4.0 \second$.
}
\end{figure}
Figure \ref{fig:conversion} shows the estimated \Ni{56} yields
across the range of masses burned to IGE
for all C-O and C-O-Ne realizations at the end
of the simulations ($4.0 \second$),
at which point the total mass burned to \Ni{56} had become constant.
The difference between the two sets of results is more pronounced
than the difference between hybrid and traditional C/O models
found by \citet{willcoxetal2016}. This difference follows from
differences in the electron capture rates, which follow from
{\color{red} two} reasons. {\color{red} HIGHER CENTRAL DENSITY?
MORE METALLICIY? HELP!}
%The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons.
%First is that higher critical density leads to higher electron capture resulting in less N\Ni{56}i56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
%NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
%hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18

>>>>

\title{Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White
Dwarf Progenitors That Have Mixed During Cooling}

@@

\begin{abstract}
The creation of ``hybrid" white dwarfs, made of a C/O
core within a O/Ne shell has been proposed, and studies indicate that
ignition in the C-rich central region makes these
viable progenitors for thermonuclear (type Ia) supernovae.
Recent work found that the C/O core is mixed with the surrounding O/Ne
as the white dwarf cools prior to accretion, which results in lower central
C fractions in the massive progenitor than previously assumed. To further
investigate the efficacy of hybrid white dwarfs as progenitors of
thermonuclear supernovae, we performed simulations of thermonuclear
supernovae from a new series of hybrid progenitors that include the
effects of mixing during cooling. The progenitor white dwarf model
was constructed with the one-dimensional stellar evolution code MESA and
represented a star evolved through the phase of unstable interior mixing
followed by accretion until it reached conditions for the ignition of
carbon burning. This MESA model was then mapped to a two-dimensional initial
condition for explosions simulated with \FLASH. For comparison, similar
simulations were performed for a traditional C/O progenitor
white dwarf. By comparing the yields of the explosions, we find that, as
with earlier studies, the lower C abundance in the hybrid progenitor compared
to the traditional C/O progenitor leads to a lower average yield of $^{56}$Ni.
Although the unmixed hybrid WD showed a similar decrement also in total iron
group yield, the mixed case does not.  We attribute this to the higher
central density required for ignition.
\end{abstract}

@@

@@

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:conversion}
Estimated yield of \Ni{56} as a function of final mass burned to IGE
for C-O-Ne progenitors (red) and C-O progenitors (blue) at
$t = 4.0 \second$.
TODO: add lines from Willcox et al.
}
\end{figure}
Figure \ref{fig:conversion} shows the estimated \Ni{56} yields
across the range of masses burned to IGE
for all C-O and C-O-Ne realizations at the end
of the simulations ($4.0 \second$),
at which point the total mass burned to \Ni{56} had become constant.
The difference between the two sets of results is more pronounced
than the difference between hybrid and traditional C/O models
found by \citet{willcoxetal2016}. This difference follows from
differences in the electron capture rates, which follow from
{\color{red} two} reasons. {\color{red} HIGHER CENTRAL DENSITY?
MORE METALLICIY? HELP!}
%The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons.
%First is that higher critical density leads to higher electron capture resulting in less N\Ni{56}i56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
%NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
%hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18
